### 2019-06-12 doc/chapters/conclusion.tex
changed conclusion

As we saw, it is really hard to verify software not written with verification in mind.
It needs a lot of changes in the software because verification is mathematical and the current software is written mostly in object-oriented style.
Software written in the functional paradigm would be much easier to reason about.

@@

The code we verified in the previous chapter is not the original code from Bitcoin-S.
So we can not guarantee the correctness of the addition of Satoshis with zero in Bitcoin-S.
Not all changes we made were as trivial as the replacement of objects with case objects.
For these non-trivial changes, as seen in section \ref{sec:bound_check}, we cannot say whether they are equivalent to the original implementation or not.

>>>>

Because of the limitations of the verication tool, we could only verify a rewritten version of the original Bitcoin-S code.
So we can not guarantee the correctness of the addition of Satoshis with zero in Bitcoin-S.
Not all changes we made were as trivial as the replacement of objects with case objects.
For these non-trivial changes, as seen for example the bound check in section \ref{sec:bound_check}, we cannot say whether they are equivalent to the original implementation or not.

So code should be written specically with formal verication in mind, in order to successfully verify it.
Otherwise, it needs a lot of changes in the software because verification is mathematical and the current software is written mostly in object-oriented style.
Software written in the functional paradigm would be much easier to reason about.

@@

Also, we found that trying to verify code reveals bugs as shown in section \ref{sec:bugfix}. Finally, our work led to some feedback to the Stainless developers to improve the tool.
